Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-11-03 ms.tex
describing how the illumination gradient was calculated

We also examine the slope and intercept of the illumination as a function of time.
It is clear that there is a gradient in the image that also correlates with the flux.
This may explain detector 490's different behavior over time.

>>>>

We also examine the slope and intercept of the illumination as a function of time.
We applying the following processing steps:
\begin{enumerate}
	\item Apply side and top reference pixels to all frames
	\item	Calculate slope images from ramp images using \texttt{ncdas}
	\item Subtract 1/f noise with a row-by-row subtraction by the average of un-illuminated pixels
	\item Calculate an average flat field over the entire time series of illuminated ata
	\item Divide each image by the flat field
	\item Collapse the illuminated region along the Y direction to make an illumination profile
	\item Fit the illumination profile to a line and save the slope and intercept
\end{enumerate}
Figure \ref{fig:illumGradientChangeOverTime} shows the slope and intercept calculated for the illumination profile over time.
It is clear that there is a gradient in the image that also correlates with the flux.
This may explain detector 490's different behavior over time.
